Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-03 Article.tex
Robust command for comment in the text

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

Dynamic recrystallization is a significant phenomenon for regulating a material's microstructure and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind.

In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
We obtain the parameters of the JMAK model through a two-step process.
First, critical stresses and strains are determined using the ANN model to filter curves effectively.
Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization.

@@

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Wan-2017}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
The steady stress is considered as the minimum one after the peak stress.
It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{Chen-2014,Li-2019,Wang-2021}:
\begin{equation}
\begin{cases}
\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
\end{cases}
\label{eq:paramsZ}
\end{equation}
With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later.

>>>>

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}
\DeclareRobustCommand{\PTM}[1]{~\begingroup\sethlcolor{green}\textcolor{red}{\hl{\textbf{P.T.M.:} #1}}\endgroup~}

@@

\PTM{The following two paragraphs will be removed}

\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.

\textcolor{red}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
We obtain the parameters of the JMAK model through a two-step process.
First, critical stresses and strains are determined using the ANN model to filter curves effectively.
Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization}.

@@

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Avrami-1939} , commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
The steady stress is considered as the minimum one after the peak stress.
It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$ \cite{Zenner-1944}, according to the following equation \cite{Chen-2014,Li-2019,Wang-2021}:
\begin{equation}
\begin{cases}
\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
\end{cases}
\label{eq:paramsZ}
\end{equation}
With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later and the effective activation energy parameter $Q$ value is $437.385$ kJ.mol$^{-1}$.
